Investigating Fault-Proneness Through Hotfix Commits in the Light of Different Programming Languages

### 2016-02-19 msr_paper/main.tex
fixing FIXMEs and adding a paper to references

\subsection{Dataset}
The SourceForge13 Dataset is selected for this study. It consists of \FIXME{[totalnumberofprojects]} projects, selected from the top 16 most popular project types in the SourceForge dataset. That enables us to differentiate results for the different kinds of projects.

@@

From Table \ref{tab:1}, \textbf{the most widely used languages from the list is Java which appears in all the 16 categories.} C, and C++ share the second place with occurrence in 15 out of 16 categories. While C++ is not present in Site Management, C is not present in Frameworks. The rest of the languages in the list are present in 10 categories on average. However, it is interesting to note that the majority of these languages are not used in Testing, which contains only Java, C, and C++. Similarity, only a few languages appears in Code Generators and Site Management categories. The observations made are reasonable since using these languages in such categories is very uncommon. \FIXME{Citation here?}

@@

Due to our criteria of selecting the languages, the chosen 8 languages are all either procedural or scripting, but not functional. Most probably this was due to the fact that functional languages are limited to specific use cases and as such are not widely popular across different domains. \FIXME{citation here?} Consequently, we compare only Procedural and Scripting languages.

>>>>

\subsection{Dataset}
The SourceForge13 Dataset is selected for this study. It consists of \textbf{49865} projects, selected from the top 16 most popular project types in the SourceForge dataset. That enables us to differentiate results for the different kinds of projects.

@@

From Table \ref{tab:1}, \textbf{the most widely used languages from the list is Java which appears in all the 16 categories.} C, and C++ share the second place with occurrence in 15 out of 16 categories. While C++ is not present in Site Management, C is not present in Frameworks. The rest of the languages in the list are present in 10 categories on average. However, it is interesting to note that the majority of these languages are not used in Testing, which contains only Java, C, and C++. Similarity, only a few languages appears in Code Generators and Site Management categories.

@@

Due to our criteria of selecting the languages, the chosen 8 languages are all either procedural or scripting, but not functional. Most probably this was due to the fact that functional languages are limited to specific use cases and as such are not widely popular across different domains  \cite{Wadler1999}. Consequently, we compare only Procedural and Scripting languages.
